### 2024-07-07 causal-inference.qmd
20240706 - wording tweaks

## Correlation Does Not Imply Causality {#sec-correlationCausality}

@@

The second criterion involves association.
The purported cause must be associated with the purported effect.
Nevertheless, as the maxim goes, "correlation does not imply causality."
Just because two variables are correlated does not necessarily mean that they are causally related.
However, correlation is useful because causality requires that the two processes be correlated.
That is, correlation is a necessary but insufficient condition for causality.
For instance, if sports drink consumption influences player performance, sports drink consumption must be associated with performance improvement.

>>>>

## Correlation Does Not Imply Causation {#sec-correlationCausality}

@@

The second criterion involves association.
The purported cause must be associated with the purported effect.
Nevertheless, as the maxim goes, "correlation does not imply causation."
Just because two variables are correlated does not necessarily mean that they are causally related.
However, correlation is useful because causality requires that the two processes be correlated.
That is, correlation is a necessary but insufficient condition for causality.
For instance, if sports drink consumption influences player performance, sports drink consumption must be associated with performance improvement.

### 2024-07-07 correlation.qmd
20240706 - wording tweaks

Correlation is an index of the association between variables.
The correlation coefficient ($r$) ranges from −1 to +1, and indicates the sign and magnitude of the association.
Although correlation does not imply causality, identifying associations between variables can still be useful because association is a necessary (but insufficient) condition for causality.

>>>>

Correlation is an index of the association between variables.
The correlation coefficient ($r$) ranges from −1 to +1, and indicates the sign and magnitude of the association.
Although correlation does not imply causation, identifying associations between variables can still be useful because association is a necessary (but insufficient) condition for causality.
